Infant Birth Weight in Brazil

### 2024-11-01 code/analysis-code/fullanalysis-v1.qmd
RRSSM1
Updated code that stopped working. Included Brazilian/non-Brazilian subsample missing code.

# Filter data based on desired conditions
filtered_data <- ML_linear %>%
  filter(Brazilian == "Brazilian")

@@

# Save regression output into table
saveRDS(ML_lm1_sub_table, file = here::here("results", "tables", "ML_lm1_sub_table.rds"))
```
```{r, message=FALSE,  warning=FALSE}
# Model 2: Sub-sample multivariate model (ML_lm2_sub)
# Filter data based on desired conditions
filtered_data <- ML_linear %>%
  filter(Brazilian == "Brazilian")

>>>>

# Filter data based on desired conditions
filtered_data <- ML_linear %>%
  filter(Brazilian == "yes")

@@

# Save regression output into table
saveRDS(ML_lm1_sub_table, file = here::here("results", "tables", "ML_lm1_sub_table.rds"))
```
```{r, message=FALSE,  warning=FALSE}
# Model 2: Sub-sample multivariate model (ML_lm2_sub)
# Filter data based on desired conditions
filtered_data <- ML_linear %>%
  filter(Brazilian == "yes")

### 2024-11-01 code/eda-code/eda-v1.qmd
RRSSM1
Updated code that stopped working. Included Brazilian/non-Brazilian subsample missing code.

For the `Nationality` variable, I combine all European nationalities into one category, "European", all Latin American nationalities into "Latin American", and all Middle Eastern nationalities into "Middle Eastern". I am combining categories because for many of the `European` and `Latin American` categories, there were very few observations. Moreover, I am interested in immigration as a general status rather than the relationship between specific immigrant countries and health status in Brazil. "Brazilian" will remain the same.

@@

```{r}
# Create dummy variables
# Check pre-structure
str(ML_linear)

# Create dummy variables for color and change to English using recode factor from dplyr
ML_linear$ModifiedColor <- factor(ifelse(ML_linear$Color %in% c("Black", "Mixed Race"), "Afro-Descent", "Euro-Descent"))

# Create dummy variables for status and change to English
ML_linear$ModifiedStatus <- recode_factor(ML_linear$Status, "Secundigesta" = "Multiparous", "Trigesta" = "Multiparous", "Multigesta" = "Multiparous", "Secundipara" = "Multiparous", "Multipara" = "Multiparous", "Primigesta" = "Nulliparous", "Nulipara" = "Nulliparous", "Primipara" = "Nulliparous")

# Create dummy variables for nationality and change to English
ML_linear$ModifiedNationality <- factor(case_when(
  ML_linear$Nationality %in% c("German", "Austrian", "Spanish", "French", "Italian", "Polish", "Portuguese", "Romanian", "Russian", "Swiss") ~ "European",
  ML_linear$Nationality %in% c("Argentine", "Paraguayan", "Uruguayan") ~ "Latin American",
  ML_linear$Nationality == "Brazilian" ~ "Brazilian",
  ML_linear$Nationality == "Syrian" ~ "Middle Eastern"
))

@@

str(ML_linear)

>>>>

For the `Nationality` variable, I combine all European nationalities into one category, "European", all Latin American nationalities into "Latin American", and all Middle Eastern nationalities into "Middle Eastern". I am combining categories because for many of the `European` and `Latin American` categories, there were very few observations. Moreover, I am interested in immigration as a general status rather than the relationship between specific immigrant countries and health status in Brazil. "Brazilian" will remain the same. I also create a dummy variable to check for collinearity between immigration status and skin color. I create a `Brazilian` variable (yes/no), and then I run a sub-sample analysis dropping all non-Brazilians.

@@

```{r}
# Check pre-structure
str(ML_linear)

@@

# Create new variables
ML_linear <- ML_linear %>%
  mutate(
    ModifiedColor = factor(ifelse(Color %in% c("Black", "Mixed Race"), # dummy variables for color and change to English
                                 "Afro-Descent", "Euro-Descent"),
                          levels = c("Euro-Descent", "Afro-Descent")),
    ModifiedStatus = factor(case_when( # dummy variables for status and change to English
      Status %in% c("Secundigesta", "Trigesta", "Multigesta", "Secundipara", "Multipara") ~ "Multiparous",
      Status %in% c("Primigesta", "Nulipara", "Primipara") ~ "Nulliparous",
      TRUE ~ NA_character_
    ), levels = c("Nulliparous", "Multiparous")),
    ModifiedNationality = factor(case_when( # dummy variables for nationality and change to English
      Nationality %in% c("German", "Austrian", "Spanish", "French", "Italian", 
                        "Polish", "Portuguese", "Romanian", "Russian", "Swiss") ~ "European",
      Nationality %in% c("Argentine", "Paraguayan", "Uruguayan") ~ "Latin American",
      Nationality == "Brazilian" ~ "Brazilian",
      Nationality == "Syrian" ~ "Middle Eastern",
      TRUE ~ NA_character_
    ), levels = c("Brazilian", "European", "Latin American", "Middle Eastern")),
    Brazilian = factor(ifelse(ModifiedNationality == "Brazilian", # create dummy variable for Brazilian/non-Brazilian to check for collinearity between skin color and immigration status
                             "yes", "no"),
                      levels = c("yes", "no"))
  )

# Verify the new structure
str(ML_linear)

### 2024-11-01 products/manuscript/Manuscript_Final_SSM.qmd
RRSSM1
Updated code that stopped working. Included Brazilian/non-Brazilian subsample missing code.

---
title: "Infant Birth Weight in Brazil"
subtitle: "A Cross-Sectional Historical Approach"
author: Cassia Roth
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
    bibliography: ../../assets/Mada_Bib.bib
    csl: ../../assets/vancouver.csl
    suppress-bibliography: false
---

>>>>

---
title: "Infant Birth Weight in Brazil"
subtitle: "A Cross-Sectional Historical Approach"
author: Cassia Roth
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
    bibliography: ../../assets/Mada_Bib.bib
    csl: ../../assets/apa.csl
    suppress-bibliography: false
---
